---
title: "project 8"
output: html_document
author: "Ebrahim kamal"
---
#Introduction
  Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement – a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://web.archive.org/web/20161224072740/http:/groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset).

#Data
Data

The training data for this project are available here:

https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv

The test data are available here:

https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv

The data for this project come from this source: http://web.archive.org/web/20161224072740/http:/groupware.les.inf.puc-rio.br/har. If you use the document you create for this class for any purpose please cite them as they have been very generous in allowing their data to be used for this kind of assignment.

#load library
```{r,eval=FALSE}
  library(caret)
```

# read train and test data
```{r,eval=FALSE}
  training <- read.csv('C:/Users/ibrahim/Desktop/P8 week 4/pml-training.csv')
  testing  <- read.csv('C:/Users/ibrahim/Desktop/P8 week 4/pml-testing.csv')
```


#clean data
```{r,eval=FALSE}
# remove first column 
training <- training[c(2:160)]
# get columns name and save it in colsNames var
ColsNames <- names(training)
# number of rows
lenCol = 19622
# start count 
count = 1
for (colName in ColsNames) {
  # get the col with name 
  currentCol = training[colName]
  currentCol = currentCol[[colName]]
  # get number NAs Value in column [1]
  lenNA   = length(subset(currentCol , is.na(currentCol)))
  # check is type of col is factor
  if(is.factor(currentCol)){
    # convert type from factor to str 
    colAsStr <- as.character(currentCol)
    #get number empty Value in column [2]
    lenSpace <- length(subset(colAsStr , colAsStr == ""))
    # sum [1] and [2]
    lenNA = lenNA + lenSpace  
  }
  #check if number of rows is bigger than 30% that has empty or NA value 
  if(((lenNA / lenCol) * 100) < 30)
  {
    # check is not str
    if(!is.character(currentCol)){
        #check is newTraining 
        if(exists('newTraining'))
        {
          # save col name in colN(list) 
          colN[count] = colName
          # add new col in data frame
          newTraining <- cbind(newTraining , new = currentCol)  
        }
        else
        {
          # save col name in colN(list) 
          colN = colName
          # create data frame
          newTraining <- data.frame(new = currentCol)
        }
        # name data frame cols  
        colnames(newTraining) <- colN
        # increase count
        count = count + 1
    }
  }
}

```

#split train data
```{r,eval=FALSE}
# split data into two variable (trainSet , testSet)
intrain <- createDataPartition(newTraining$classe , p= 0.6,list = T)
trainSet <- newTraining[intrain[[1]],]
testSet <- newTraining[-intrain[[1]],]
```

#prepare testset
```{r,eval=FALSE}
newTesting <- testing[colnames(newTraining)[1:(dim(newTraining)[2] - 1)]]
```

#training
```{r,eval=FALSE}
mod_1  = train(classe ~ . , mathod = 'rf',data = trainSet)
pred_1 = predict(mod_1,testSet)
mod_2  = train(classe ~ . , mathod = 'glm',data = trainSet)
pred_2 = predict(mod_2,testSet)
mod_3  = train(classe ~ . , mathod = 'gam',data = trainSet)
pred_3 = predict(mod_3,testSet)
all_pred <- data.frame(pred1 = pred_1,pred2 = pred_2,pred3 = pred_3)
pred_All = predict(all_pred,newTesting)
```

#Accuracy
```{r,eval=FALSE}
# get rf accuracy
acc_1 <- (table(as.character(pred_1) == as.character(testSet$classe))[2]/length(as.character(pred_1)))[[1]]
# get glm accuracy
acc_2 <- (table(as.character(pred_2) == as.character(testSet$classe))[2]/length(as.character(pred_1)))[[1]]
# get gam accuracy
acc_3 <- (table(as.character(pred_3) == as.character(testSet$classe))[2]/length(as.character(pred_1)))[[1]]
# get combine classification accuracy
acc_All <- (table(as.character(pred_All) == as.character(testSet$classe))[2]/length(as.character(pred_1)))[[1]]
```

#get class for test dataSet

```{r,eval=FALSE}
#select the big accuracy and use it to predict class
if(acc_1 > acc_2 && acc_1 > acc_3 && acc_1 > acc_All){
  predict(mod_1,testing)
}else if(acc_2 > acc_3 && acc_2 > acc_All){
  predict(mod_2,testing)
}else if(acc_3 > acc_All){
  predict(mod_3,testing)
}else{
  predict(mod_All,testing)
}
```



